problem years

### 2024-08-12 src/oa_RF_corrected.Rmd
corrected regions

@@

  #file <- paste0(path, "/outputs/rf/models/oa_rf/regions/region_", as.character(i), ".RData")
  file <- paste0("/hdd/tmp/regions/region_", as.character(i), ".RData")  
  save(model.all, file = file)  # file name = region not in the training data
  rm(model.all)

@@

### Resamples for plots

```{r, eval=F}
# create a list of the above model outputs
filenames <- list.files(paste0(path, "/outputs/rf/models/oa_rf/regions"), pattern = "*.RData", full.names = T)

for (i in filenames){
  load(file = i)
  i <- gsub("/home/nw19521/projects/web.diffusion/outputs/rf/models/oa_rf/regions/|.RData", "", i)
  assign(i, model.all)  
}

 fit.model.all <- mget(ls(pattern = "^region_"))

# clear up
rm(model.all) # this is the last item from the loop
rm(list = ls(pattern = "^region_"))

# resamples
fit.model.all.res <- resamples(fit.model.all)
summary(fit.model.all.res)

# plot metrics

# TODO: fix the year labels

scales <- list(x=list(relation="free"), y=list(relation="free"))
bwplot(fit.model.all.res, scales=scales)

# TODO: fix the year labels
```

### Variable importance

```{r, eval=F, include=TRUE, results= 'markup', message=FALSE}
lapply(names(fit.model.all), function(x) plot(varImp(fit.model.all[[x]]), main=as.character(x)))
```

```{r, eval=F}
help <- lapply(fit.model.all, function(x) varImp(x)) 
help <- lapply(help, function(x) x[[1]])
help <- do.call("rbind", help)

importance <- help %>% rownames_to_column() %>% 
  mutate(feature = gsub("model.all[0-9]+.", "", rowname),
         year = gsub(".*?([0-9]+).*", "\\1", rowname)) %>% 
  rename(importance = Overall) %>% 
  relocate(importance, .after = year) %>% 
  dplyr::select(-rowname)

importance %>% ggplot() +
  geom_line(aes(x=year, y = importance, color = feature, group = feature), size = 1) +
  scale_color_discrete(name = "Features") +
  #scale_linetype_manual(name = "Website density regressions111") 
  ylab("Importance") + 
  ggtitle("Feature importance") +
  theme_minimal() +
  theme(axis.title.x=element_blank(),
        plot.title = element_text(hjust = 0.5))

```

@@

new.path <- "/hdd/tmp/regions/"
#filenames <- list.files(paste0(path, "/outputs/rf/models/oa_rf/regions"), pattern = "*.RData", full.names = T)

@@

for (i in regions){
  load(file = paste0(new.path, "region_", as.character(i), ".RData"))
  #model.name <- gsub("/home/nw19521/projects/web.diffusion/outputs/rf/models/oa_rf/regions/|.RData", "", i)
  #assign(as.character(i), model.all)

@@

path.out <- paste0(path, "/outputs/rf/figures/test_regions_OA.csv")
rf.year.all.metrics %>% 
  as.data.frame() %>%
  rownames_to_column(var = "metrics") %>% 
  pivot_longer(!metrics, names_to = "train.test") %>% 
  pivot_wider(names_from = metrics, values_from = value) %>% 
  separate(train.test, c("train", "test"), remove = F) %>% 
  # left_join(lookup.region, by = c("train" = "RGN11CD")) %>% 
  # rename(train.region=RGN21NM) %>% 
  left_join(lookup.region, by = c("test" = "RGN11CD")) %>% 
  rename(test.region=RGN21NM) %>% 
  arrange(Rsquared) %>% 
  dplyr::select(test.region, Rsquared) %>% 
  write_csv(path.out)
```

>>>>

64 GB of swap memory to run the below

@@

  #file <- paste0(path, "/outputs/rf/models/oa_rf/regions/region_", as.character(i), ".RData")
  file <- paste0("/hdd/tmp/regions/corrected/regions_corrected_", as.character(i), ".RData")  
  save(model.all, file = file)  # file name = region not in the training data
  rm(model.all)

@@

@@

new.path <- "/hdd/tmp/regions/corrected/"
#filenames <- list.files(paste0(path, "/outputs/rf/models/oa_rf/regions"), pattern = "*.RData", full.names = T)

@@

  print(i)

  load(file = paste0(new.path, "regions_corrected_", as.character(i), ".RData"))
  #model.name <- gsub("/home/nw19521/projects/web.diffusion/outputs/rf/models/oa_rf/regions/|.RData", "", i)
  #assign(as.character(i), model.all)

@@

path.out <- paste0(path, "/outputs/rf/figures/test_regions_OA_corrected.csv")
rf.year.all.metrics %>% 
  as.data.frame() %>%
  rownames_to_column(var = "metrics") %>% 
  pivot_longer(!metrics, names_to = "train.test") %>% 
  pivot_wider(names_from = metrics, values_from = value) %>% 
  separate(train.test, c("train", "test"), remove = F) %>% 
  # left_join(lookup.region, by = c("train" = "RGN11CD")) %>% 
  # rename(train.region=RGN21NM) %>% 
  left_join(lookup.region, by = c("test" = "RGN11CD")) %>% 
  rename(test.region=RGN21NM) %>% 
  arrange(Rsquared) %>% 
  dplyr::select(test.region, Rsquared) %>% 
  write_csv(path.out)
```

### 2024-08-12 src/oa_RF_corrected_10.Rmd
corrected regions

THE BELLOW HAS NOT BEEN RUN NEITHER THE FILENAMES HAS BEEN CHANGED (add: _corrected)

@@

@@

  #file <- paste0(path, "/outputs/rf/models/oa_rf/regions/region_", as.character(i), ".RData")
  file <- paste0("/hdd/tmp/regions/region_", as.character(i), ".RData")  
  save(model.all, file = file)  # file name = region not in the training data
  rm(model.all)

@@

@@

@@

new.path <- "/hdd/tmp/regions/"
#filenames <- list.files(paste0(path, "/outputs/rf/models/oa_rf/regions"), pattern = "*.RData", full.names = T)

@@

for (i in regions){
  load(file = paste0(new.path, "region_", as.character(i), ".RData"))
  #model.name <- gsub("/home/nw19521/projects/web.diffusion/outputs/rf/models/oa_rf/regions/|.RData", "", i)
  #assign(as.character(i), model.all)

@@

  rm(model.all)
}

@@

path.lookup <- paste0(path, "/data/raw/Local_Authority_District_to_Region_(April_2021)_Lookup_in_England.csv")  
lookup.region <- read_csv(path.lookup) %>% 
  dplyr::select(RGN21CD, RGN21NM) %>% 
  distinct() %>% 
  rename(RGN11CD = RGN21CD) %>% 
  add_row(RGN11CD = c("Scotland", "NI", "Wales"), 
          RGN21NM = c("Scotland", "Nortern Ireland", "Wales"))

path.out <- paste0(path, "/outputs/rf/figures/test_regions_OA.csv")
rf.year.all.metrics %>% 
  as.data.frame() %>%
  rownames_to_column(var = "metrics") %>% 
  pivot_longer(!metrics, names_to = "train.test") %>% 
  pivot_wider(names_from = metrics, values_from = value) %>% 
  separate(train.test, c("train", "test"), remove = F) %>% 
  # left_join(lookup.region, by = c("train" = "RGN11CD")) %>% 
  # rename(train.region=RGN21NM) %>% 
  left_join(lookup.region, by = c("test" = "RGN11CD")) %>% 
  rename(test.region=RGN21NM) %>% 
  arrange(Rsquared) %>% 
  dplyr::select(test.region, Rsquared) %>% 
  write_csv(path.out)
```

>>>>

@@

```{r}
rm(list=setdiff(ls(), c("df", "path")))
```

64 GB of swap memory to run the below

@@

  #file <- paste0(path, "/outputs/rf/models/oa_rf/regions/region_corrected_", as.character(i), ".RData")
  file <- paste0("/hdd/tmp/regions/corrected_10/regions_corrected_10", as.character(i), ".RData")  
  save(model.all, file = file)  # file name = region not in the training data
  rm(model.all)

@@

THE RESULTS ARE WEIRD. REVISIT.

@@

# correct for non-England file names
df <- df %>% 
  mutate(RGN11CD = ifelse(RGN11CD == "Wales", "W0",
                          ifelse(RGN11CD == "Scotland", "S1",
                                 ifelse(RGN11CD == "NI", "N0", RGN11CD))))

@@

new.path <- "/hdd/tmp/regions/corrected_10/"
#filenames <- list.files(paste0(path, "/outputs/rf/models/oa_rf/regions"), pattern = "*.RData", full.names = T)

@@

  print(i)

  load(file = paste0(new.path, "regions_corrected_10", as.character(i), ".RData"))
  #model.name <- gsub("/home/nw19521/projects/web.diffusion/outputs/rf/models/oa_rf/regions/|.RData", "", i)
  #assign(as.character(i), model.all)

@@

  rm(model.all)

  print(i)

@@

path.lookup <- paste0(path, "/data/raw/Local_Authority_District_to_Region_(April_2021)_Lookup_in_England.csv")  
lookup.region <- read_csv(path.lookup) %>% 
  dplyr::select(RGN21CD, RGN21NM) %>% 
  distinct() %>% 
  rename(RGN11CD = RGN21CD) %>% 
  add_row(RGN11CD = c("S1", "N0", "W0"), 
          RGN21NM = c("Scotland", "Nortern Ireland", "Wales"))

path.out <- paste0(path, "/outputs/rf/figures/test_regions_OA_corrected_10.csv")
rf.year.all.metrics %>% 
  as.data.frame() %>%
  rownames_to_column(var = "metrics") %>% 
  pivot_longer(!metrics, names_to = "train.test") %>% 
  pivot_wider(names_from = metrics, values_from = value) %>% 
  separate(train.test, c("train", "test"), remove = F) %>% 
  # left_join(lookup.region, by = c("train" = "RGN11CD")) %>% 
  # rename(train.region=RGN21NM) %>% 
  left_join(lookup.region, by = c("test" = "RGN11CD")) %>% 
  rename(test.region=RGN21NM) %>% 
  arrange(Rsquared) %>% 
  dplyr::select(test.region, Rsquared) %>% 
  write_csv(path.out)
```

### 2024-08-12 src/problem_years_10.Rmd
corrected regions

path.out <- paste0(path, "/outputs/pc_year_1.png")
ggsave(path.out, bg='#ffffff')  
```

@@

path.out <- paste0(path, "/outputs/pc_year_1_corrected.png")
ggsave(path.out, bg='#ffffff')  
```

>>>>

path.out <- paste0(path, "/outputs/pc_year_10.png")
ggsave(path.out, bg='#ffffff')  
```

@@

path.out <- paste0(path, "/outputs/pc_year_10_corrected.png")
ggsave(path.out, bg='#ffffff')  
```
